% Halloween at the Barrowmaze
% Copyright (c) 2022-2023 Peter H. Froehlich <peter.hans.froehlich@gmail.com>.
% License terms: CC BY-SA 4.0

\section{Halloween at\\ the Barrowmaze}
\label{halloween}
I wanted to spice up our Barrowmaze game a little, so I decided that all games
in October 2022 would be ``Red October'' games and that October 31, 2022 would
be a ``Halloween Special.'' It was important to set up ``Red October'' first to
prepare players for the \emph{really} weird stuff that was to come, so here's a
summary of both. Feel free to rip this off if you also have players who are
generally amenable to occasional silliness.

\textbf{Red October}

Every year in October, the sky over the Barrowmoor turns red and stranger than
usual things go on below. I used the moderately terrifying ``Pit of Chaos''
table from the actual module, but you can substitute any super-dangerous ``what
terrible monster gates in from the depths of hell'' table you have handy.

Before each session I rolled a d6 to determine how many things gate in: 1--3 only
one, 4--5 two, 6 three. Then I placed whatever it was in a random location; I
simply rolled d100 for a room but I only allowed rooms that had previously been
explored; if the room had not been explored, I divided the room number by 2; and
if that room didn't make sense, I picked the next lower room number that did.

For the October 3, 2022 session the d6 came up 1, so only a single ``gate'' roll
was required; 4 ghouls gated in; I rolled room 80 but that wasn't explored; room
40 didn't make sense (behind a secret door ghouls wouldn't know how to operate);
so room 39 it was.
%
Interestingly room 39 already had a large group of tomb robbers from a previous
restock roll, so I conducted that fight to see who'd win; the tomb robbers barely
survived. In game I had the players stumble into the tail-end of the fight which
meant the tomb robbers were ``on edge'' and almost attacked the player
characters, accusing them of ``sending'' those ghouls their way.

Other ``Red October'' sessions added even more ghouls, a banshee, and a ghast
to various rooms; those ghouls are actually still haunting a section of the
Barrowmaze to this day, but the ghast and the banshee have since been taken out.
Luckily I never rolled 1--4 bone devils\dots{}

\textbf{Halloween Special}

For the October 31, 2022 session, not only was the sky red, but it was also
dark around the Barrowmoor, regardless of the actual time of day. The path to
the central mound had ``pumpkin lamps'' at regular intervals; a little bit off
the path, skeletons, zombies, and large spiders (illusions, but whatever) could
be seen ``threathening'' the path; weird organ music and the occassional scream
or evil laughter were heard as well.

There was a table out front next to the entrance to the central mound; one banner
read ``One Night Only!'' the other said ``Final Halloween Raffle!'' There was a
vampire sitting here, one ``Strump von Wasilatsch,'' with all the usual vampire
equipment (pale, well dressed, red-lined cape, the works). He also had four dire
wolves resting behind him, one of which was in fact another vampire. Strump was
wearing a ``VBS'' (``Vampyre Benevolent Society'') pin and had a bottle of red
wine that he kept using to top off his glass; he got up as player characters
approached to give his spiel:

\begin{itemize}

\item ``Ah, welcome, welcome adventurers! I am Count von Wasilatsch and I am
  here from the VBS for our special \emph{One Night Only Final Halloween Raffle}.
  Your donations will go to worthy causes completely and utterly of our choosing,
  but the raffle tickets we have promise \emph{amazing} things, just \emph{perfect}
  for the likes of you who are about to head underground to \dots{} \emph{vanquish}
  \dots{} evil?''

\item ``Ah, the tickets, yes! Green tickets are 5gp, yellow tickets are 20gp,
  and red tickets, our biggest item tickets, those are 100gp. Buy for yourself,
  buy for your friends, you will \emph{not} regret it! If you truly are
  \emph{adventurers} that is?''

\item He then mumbles ``Certain undisclosed rules and restrictions apply,
  parents are responsible for their children, not valid after October 31, only
  one purchase per entity, all sales are final, void where prohibited by law or
  decree.'' and smiles, fangs and all.

\end{itemize}

If player characters come back for more tickets later, he says ``only one
purchase per entity'' and smiles; if they persist one dire wolf growls and he
shushes it, still smiling; if they persist he says ``only one purchase, really,
get out of here before it gets mad!'' and keeps smiling; after that the dire
wolf would strike once but he would rein it in after that ``get out of here!''
no longer smiling; more of that and they all attack, slaughtering the player
characters.

Going down the stairs in the central mound, it is clear that there are more
pumpkin-based light sources ahead; indeed the whole 60'\(\times\)60' chamber
appears to have been cleared and tables have been set up against the north,
south, and east wall. Behind each table is another vampire, although these are
not as talkative; the table to the north has a green banner, the one to the
south has a yellow banner, and the one to the east has a red banner; three more
dire wolves skulk around here and there; behind each table is a chest with a
big lock, that's where the stuff is stored. For each ticket a player has, let
them roll once on the table below.

What's with the ``Marshmellow d66?'' In our game, a player can \emph{once per
session} make a d20 roll with a d30 instead; this d66 allows the player to use
a d66 instead of a d20 once, after their main character consumes it. Pretty tasty!

Somewhere on each item there's a \emph{tiny} note saying ``Provided `as is'
without any express or implied warranties. Best by October 31st.'' Yes, of
course all items are good only for the one session, they crumble to dust after
midnight. Also each item has a 1\% chance of malfunctioning per use; but that
malfunction will \emph{not} be extra-detrimental to the user. (For stuff with
a duration, roll when it matters, not when it's first activated. So invisibility
will work until it doesn't.)

\end{multicols}
\begin{tabularx}{\textwidth}{cZZZ}
\textbf{Roll} & \textbf{Green/Cheap} & \textbf{Yellow/Standard} & \textbf{Red/Fancy}\\
1 & Potion Healing                   & Potion Control Undead    & Ring Regeneration\\
2 & Potion Invulnerability           & Potion Heroism           & Wand Polymorph \(\times\)6\\
3 & Potion Gaseous Form              & Potion Speed             & Wand Cold \(\times\)6\\
4 & Potion Invisibility              & Dagger+1                 & Sword+1, Flaming\\
5 & Bullet+1 \(\times\)8             & Sling+1                  & Spear+3\\
6 & Arrow+1 \(\times\)6              & Armor/Cloak+1            & Ring Telekinesis\\
7 & Scroll Magic Missile \(\times\)3 & Wand Fear \(\times\)6    & Staff Healing\\
8 & Marshmellow d66                  & Scroll Protection Undead & Gauntlets Ogre Power\\
\end{tabularx}
\begin{multicols}{2}

\textbf{So\dots{} What Happened?}

Of course the players bought only a few tickets, being suspicious of the entire
setup. Predictably, once they were downstairs and had gotten a bunch of items,
they wanted to go back for more tickets. But they got the hint and didn't push
their luck.
%
Down in the Barrowmaze I had added some sound and light effects: Instead of the
usual silence, there was a constant ``screams and evil laughter'' background,
complete with more ``haunted house'' illusions. But there were also lighted
neon signs pointing the way towards previously undiscovered magic items and
treasures.
%
The players started carefully, but after a few successful ``fights'' using
their \emph{Wand of Cold} and other items they became more confident. Until
they followed a neon sign to the old temple where a Banshee held court. They
debated what to do for at least 40 minutes, but in the end they ``chickened''
and left. Despite the fact that they could clearly see a \emph{huge} pile of
gold.

So we all learned that no amount of magic gear will make you into an
\emph{adventurer} when that's just not in your bones to begin with!
\by{phf}
\endinput
